DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-19 paper/related.tex
related work revision

In this paper, we demonstrated that a low-cost embedded platform such
as the  Raspberry Pi 3 can successfully run a CNN-based autonomous
driving control system in real-time. However, it should be noted that
the CNN we used here is relatively small compared to recent
state-of-the-art CNNs, which are increasingly larger and deeper.
For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters. Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.

@@

%% Another autonomous vehicle platform is the Donkey Car\footnote{https://donkeycar.com}.
%% Like the DeepPicar, the Donkey Car is a low cost platform that can be 
%% utilized for researching self-driving cars. However, comparatively, the
%% DeepPicar is approximately \$200 cheaper than the Donkey Car. 
%% Furthermore, the Donkey Car was created with an emphasis on model accuracy
%% and the ability of the car to navigate the desired environment. We are 
%% more focused on the real-time performance of the DeepPicar, and whether
%% the Raspberry Pi 3 embedded computing platform can properly support autonomous 
%% vehicle operations. To the best of our knowledge, no other studies have
%% been done to evaluate the capabilities of the Pi 3 for running DNNs and
%% performing autonomous vehicle operations.

>>>>

There are several relatively inexpensive RC-car based autonomous car
testbeds. MIT's RaceCar~\cite{shin2017project} and UPenn's
F1$/$10~\cite{upennf1tenth} are both based on a Trexx 1/10 scale RC
car and a powerful NVIDIA Jetson computing platform equipped with many
sophisticated sensor packages such as a lidar. However, they both cost
more than \$3,000, requiring considerable
investment. DonkeyCar~\cite{donkeycar} is similar to our DeepPicar as
it also uses a Raspberry Pi 3 and a CNN for end-to-end control,
although it costs slightly more because it uses a more expensive 1/16
scale RC car. The main contribution of our paper is not the hardware
design but in the detailed analysis of computational characteristics
for the CNN-based end-to-end real-time control.

In this paper, we have analyzed real-time performance of a
state-of-the art CNN, used in NVIDIA's DAVE-2 self-driving car, on a
low-cost raspberry pi 3 quad-core platform. It should be noted,
however, that DAVE-2's CNN we used here is relatively small compared
to recent state-of-the-art CNNs, which are increasingly larger and
deeper. For example, the CNN based object detector models evaluated in
Google's recent study~\cite{huang2017speed} have between 3M to 54M
parameters. Using such large CNN models will be challenging on
resource constrainted embedded computing platforms, especially for
real-time applications such as self-driving cars.

@@

%% and the ability of the car to navigate the desired environment. We are 
%% more focused on the real-time performance of the DeepPicar, and whether
%% the Raspberry Pi 3 embedded computing platform can properly support autonomous 
%% vehicle operations. To the best of our knowledge, no other studies have
%% been done to evaluate the capabilities of the Pi 3 for running DNNs and
%% performing autonomous vehicle operations.
